A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-08 main.tex
Preliminaries

\subsection{Counting string lengths}

@@

\subsection{Satisfying Constraints on Occurrence of Letters}\label{sec:introduction:parikh}

@@

Finally, we sometimes refer to a structure-preserving map between two monoids
$\Monoid_1, \Monoid_2$ as a \textit{homomorphism} between $\Monoid_1$ and
$\Monoid_2$, that is a map $\Map : S_1 \rightarrow S_2$ such that $\Map(a
\MonoidOp_1 b) = \Map(a) \MonoidOp_2 \Map(b)$, where $S_1, S_2$ are the carrier
sets of $\Monoid_1$ and $\Monoid_2$ respectively, and $\MonoidOp_1, \MonoidOp_2$
their binary operations.

@@

We define an alphabet as a set of symbols $\Alphabet$ with words $\Strings$, and
the concatenation operation as $s_1 \Concat{} s_2$ over two strings $s_1, s_2$.
Note that $\Strings = \Tuple{\Alphabet;\Concat{};\epsilon}$, is a
non-commutative monoid, referred to as the free monoid. The string length
function, $\Length{s}$ is an example of a homomorphism between $\Strings$
and~$\mathbb{Z}$.

A non-deterministic automaton~$\Automaton$ with alphabet~$\Alphabet$ is
$\AutomatonTuple$ where $\Transitions = \States \times \Alphabet \times
\States$, $\States$ is its states, $\InitialState$ is w.l.o.g. assumed to be the
single initial state, and $\AcceptingStates$ is its set of accepting states.  We
write a transition $\Transition = \Tuple{\State, \Label, \State'} \in
\Transitions$ as $\Transition = \FromLabelTo{\State}{\Label}{\State'}$.
Similarly, we use the notation $\FromLabelTo{\State}{}{}$ to refer to the set of
transitions starting in $\State$, and $\FromLabelTo{}{}{\State}$ to refer to the
set of transitions coming into $\State$, whenever the automaton is clear from
the context.

>>>>

\subsection{Counting String Lengths}

@@

\subsection{Counting Letters}\label{sec:introduction:parikh}

@@

Finally, a \textit{homomorphism} is a structure-preserving map between two monoids
$\Monoid_1, \Monoid_2$, that is a map $\Map : S_1 \rightarrow S_2$ such that $\Map(a
\MonoidOp_1 b) = \Map(a) \MonoidOp_2 \Map(b)$, where $S_1, S_2$ are the carrier
sets of $\Monoid_1$ and $\Monoid_2$ respectively, and $\MonoidOp_1, \MonoidOp_2$
their binary operations.

@@

We define an alphabet as a finite set of symbols $\Alphabet$ with words $\Strings$, and
the concatenation operation as $s_1 \Concat{} s_2$ over two strings $s_1, s_2$.
Note that $\Strings = \Tuple{\Alphabet;\Concat{};\epsilon}$, is a
non-commutative monoid, referred to as the free monoid. The string length
function, $\Length{s}$ is an example of a homomorphism between $\Strings$
and~$\mathbb{Z}$.

An automaton~$\Automaton$ with alphabet~$\Alphabet$ is
$\AutomatonTuple$ where $\Transitions \subseteq \States \times \Alphabet \times
\States$, $\States$ is its states, $\InitialState$ its
initial state, and $\AcceptingStates$ is its set of accepting states.  We
write a transition $\Transition = \Tuple{\State, \Label, \State'} \in
\Transitions$ as $\Transition = \FromLabelTo{\State}{\Label}{\State'}$.
Similarly, we use the notation $\FromLabelTo{\State}{}{}$ to refer to the set of
transitions starting in $\State$, and $\FromLabelTo{}{}{\State}$ to refer to the
set of transitions coming into $\State$, whenever the automaton is clear from
the context.
